---
title: "R Notebook"
output: html_notebook
---

Save card names with a character vector

```{r}
hand <- c("ace", "king", "queen", "jack", "ten")
hand
```

The most common attributes to give an atomic vector are names, dimensions (dim),
and classes

```{r}
names(die)
```

```{r}
names(die) <- c("one", "two", "three", "four", "five", "six")
names(die)
```

```{r}
die
names(die) <- NULL
die
```

To change the names, assign a new set of labels to names:

You can transform an atomic vector into an n-dimensional array by giving it a dimensions
attribute with dim.

```{r}
dim(die) <- c(2, 3)
die
```

```{r}
hand1 <- c("ace", "king", "queen", "jack", "ten", "spades", "spades",
"spades", "spades", "spades")

matrix(hand1, nrow = 5)
matrix(hand1, ncol = 2)
dim(hand1) <- c(5, 2)
```



Data Frame
```{r}
df <- data.frame(face = c("ace", "two", "six"),
suit = c("clubs", "clubs", "clubs"), value = c(1, 2, 3))

df
```

Save a copy of Deck as a new csv

```{r}
write.csv(deck, file = "cards.csv", row.names = FALSE)
```

```{r}
deck[1,c(1,2,3)]
```

```{r}
new <- deck[1, c(1,2,3)]
new
```

```{r}
deck[1, c(TRUE, TRUE, FALSE)]
```

```{r}
deal <- function(cards){
  cards[1, ]
}
```

```{r}
deal(deck)
```

SUFFLE THE DECK

To shuffle the deck, you need to randomly reorder the rows in the data frame.

```{r}
deck2 <- deck[1:52, ]
```

If you want the rows to come in a random order, then you need to sort the integers from 1 to 52 into a random order and use the results as a row index.

```{r}

random <- sample(1:52, size = 52)

```


```{r}
deck4 <- deck[random, ]
head(deck4)
```

```{r}
shuffle <- function(df){
  suff <- sample(1:52, size = 52)
  df[suff, ]
}
```


```{r}
shuffle(deck)
```

```{r}
deal(deck)

deck2 <- shuffle(deck)
```

```{r}
deal(deck2)
```

```{r}
deck2 <- deck
```

CHANGING VALUES IN PLACE

You can also create values that do not yet exist in your object. R will expand the object to accommodate the new values:
```{r}
deck2$new <- 1:52
head(deck2)
```

To play war, you just need to change the values of your aces from 1 to 14.

As long as you haven’t shuffled your deck, you know just where the aces are. They appear every 13 cards. Hence, you can describe them with R’s notation system:

Now all you have to do is assign a new set of values to these old values

```{r}
deck2$value[c(13, 26, 39, 52)] <- 14
```

What if you've suffled your deck?

First, build a logical test that identifies the aces in your shuffled deck:

```{r}
deck3 <- shuffle(deck)
deck3$face == "ace"
```

Then use the test to single out the ace point values. Since the test returns a logical vector, you can use it as an index:
```{r}
deck3$value[deck3$face == "ace"]

```

Finally, use assignment to change the ace values in deck3 :
```{r}
deck3$value[deck3$face == "ace"] <- 14
head(deck3)
```

In hearts, every card has a value of zero:
```{r}
deck4 <- deck
deck4$value <- 0
deck4
```

Each card in the suit of heartshas a value of 1.

```{r}
deck4$suit == "hearts"
```

Then use your test to select the value of this card
```{r}
deck4$value[deck4$suit == "hearts"]
```

Finaly assign a new number to this value
```{r}
deck4$value[deck4$suit == "hearts"] <- 1
```

In hearts, the queen of spades has the most unusual value of all: she’s worth 13 points.

You could find all of the queens:
```{r}
deck4[deck4$face == "queen", ]
```

Boolean operators combine multiple logical tests together into a single test.

You want to test each card to see if it is both a queen and a spade. You can write
this test in R with:
```{r}
deck4$face == "queen" & deck4$suit == "spades"
```

I’ll save the results of this test to its own object. That will make the results easier to work with:
```{r}
queenOfSpades <- deck4$face == "queen" & deck4$suit == "spades"
```

select the value of the queen of spades.
```{r}
deck4[queenOfSpades, ]
deck4$value[queenOfSpades] <- 13
```

```{r}
deck5 <- deck
```

```{r}
head(deck5)
```

You can change the value of the face cards in one fell swoop with %in% :
```{r}
facecard <- deck5$face %in% c("king", "queen", "jack")
```

```{r}
deck5[facecard, ]
```

```{r}
deck5$value[facecard] <- 10
head(deck5, 13)
```

```{r}
deck5$value[deck5$face == "ace"] <- NA
deck5
```

```{r}
ls(emptyenv())
ls(globalenv())
```

Every time R runs a function, it creates a new active environment to evaluate the function in

R creates a new environment each time it evaluates a function. R will use the new environment as the active environment while it runs the function


