---
title: "R Notebook"
output: html_notebook
---

Create an R object named die that contains the number one through six
```{r}
die <- 1:6
```

Roll your die and get a number back

```{r}
sample(x = die, size = 1)
```

R code that simulates rolling a pair of dice
To add up your dice, feed your result into the sum function:

```{r}
dice <- sample(die, size = 2, replace = TRUE)
dice

sum(dice)
```

Turn your dice code into a function by calling:

```{r}
roll <- function(){
  die <- 1:6
  dice <- sample(die, size = 2, replace = TRUE)
  sum(dice)
}
```

```{r}
roll()
```

Arguments:

```{r}
roll2 <- function(bones = 1:6){
  dice <- sample(bones, size = 2, replace = TRUE)
  sum(dice)
}
```

```{r}
roll2()
```

Replicate provides an easy way to repeat an R command many times.

```{r}
replicate(10, roll())
```

Simulate 10,000 dice rolls and plot the results.

```{r}
rolls <- replicate(10000, roll())
```

Each number occurs in proportion to the number of combinations that generate it.
```{r}
library(ggplot2)
qplot(rolls, binwidth = 1)
```

To weight your dice, you need to add a prob argument with a vector of weights to sample, like this:
```{r}
roll <- function() {
die <- 1:6
dice <- sample(die, size = 2, replace = TRUE,
prob = c(1/8, 1/8, 1/8, 1/8, 1/8, 3/8))
sum(dice)
}
```


```{r}
rolls <- replicate(10000, roll())
qplot(rolls, binwidth = 1)
```

The dice are now clearly biased towards high numbers, since high sums occur much more often than low sums.

